The \dealii{} Library, Version 8.5

### 2017-03-03 8.5/paper.tex
Add people who have contributed code; add funding sources.

\dealii{} is a world-wide project with dozens of contributors around the
globe. Other than the authors of this paper, the following people contributed code to
this release:
%
% get this from the changes.h file using
%   egrep '^ *\(.*201[56789]' 8.3.0-vs-8.4.0.h | perl -p -e 's/201\d.*//g; s/, */\n/g; s/^ *\(?//g;' | sort | uniq
% then sort by last name and remove the authors of this paper
%

@@

% TODO: add your funding here

T.~Heister was partially supported by the Computational Infrastructure in
Geodynamics initiative (CIG), through the National Science Foundation under Award No. EAR-0949446 and The University of California—Davis, and National Science Foundation grant DMS1522191.

>>>>

\dealii{} is a world-wide project with dozens of contributors around the
globe. Other than the authors of this paper, the following people contributed code to
this release:
%
% get this from the changes/*/* files using the command listed in the
% release-tasks paper and remove the authors of this paper
%
Rajat  Arora, 
Mauro  Bardelloni, 
Conrad  Clevenger, 
Sam  Cox, 
Juliane  Dannberg, 
Ren{\'e}  Gassm{\"o}ller, 
Joscha  Gedicke, 
Sebastian  Gonzalez-Pintor, 
Ryan  Grove, 
Michael  Harmon, 
Daniel  Jodlbauer, 
Guido  Kanschat, 
Justin  Kauffman, 
Paul  Kuberry, 
Dustin  Kumor, 
Konstantin  Ladutenko, 
Andrew  McBride, 
Mathias  Mentler, 
Andrea  Mola, 
Dragan  Nikolic, 
Vaibhav  Palkar, 
Spencer  Patty, 
Jonathan  Perry-Houts, 
Giuseppe  Pitton, 
Ce  Qin, 
Jonathan  Robey, 
Mayank  Sabharwal, 
Ali  Samii, 
Alberto  Sartori, 
Daniel  Shapero, 
Martin  Steigemann, 
Jihuan  Tian, 
Jaeryun  Yim, 
Toby  Young, 
Zhao, Liang.

@@

\marginpar{Add your funding here as appropriate}
W.~Bangerth was partially
supported by the National Science Foundation under award OCI-1148116
as part of the Software Infrastructure for Sustained Innovation (SI2)
program; and by the Computational Infrastructure in Geodynamics initiative
(CIG), through the National Science Foundation under Awards
No.~EAR-0949446 and EAR-1550901 and The University of California -- Davis.

T.~Heister was partially supported by the Computational Infrastructure in
Geodynamics initiative (CIG), through the National Science Foundation
under Award No. EAR-0949446 and The University of California -- Davis, and National Science Foundation grant DMS1522191.
